%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Ranjiraj Rajendran Nair} \\ \vspace{1pt}
    Arnold-Zweig street 30, Magdeburg 39120, Saxony-Anhalt, Germany\\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +49 1590-6347223 ~ \href{mailto:ranjiraj4141@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{ranjiraj4141@gmail.com}} ~ 
    \href{https://linkedin.com/in/reng99/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/reng99}}  ~
    \href{https://github.com/ranjiGT/}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/ranjiGT}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Otto von Guericke University}{April 2019 -- present}
      {Master of Science in Data and Knowledge Engineering}{Magdeburg, Saxony-Anhalt}
  \resumeSubHeadingListEnd

%------RELEVANT COURSEWORK-------
\section{Relevant Coursework}
    %\resumeSubHeadingListStart
        \begin{multicols}{4}
            \begin{itemize}[itemsep=-5pt, parsep=3pt]
                \item\small Data Mining
                \item Machine Learning
                \item Optimization Algorithms 
                \item Visual Analytics
                \item DevOps Technologies
                \item Data Warehouse
                \item Simulation Modeling
                \item Deep Learning 
            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}
    %\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {QualityKiosk Technologies}{Jul 2016 -- April 2018}
      {Junior Data Scientist - Department of Center of Excellence}{Navi Mumbai, India}
      \resumeItemListStart
        \resumeItem{\textbf{Housing Development Finance Corporation (HDFC) bank for Machine Learning/AI explainability with CRMNext solutions.}
        On-premise client location including different stakeholders such as performance testing, application monitoring, to identify the key performance indicators (KPIs) for adding business value for the CRM application. Key responsibilities: Perform system administration, documentation and application testing, text normalization and processing, writing NLP parsers, and spell checkers. \textit{Duration: 6 months}}
        \resumeItem{\textbf{Infrastructure Development Finance Company (IDFC) bank with MLOps and cloud service virtualization.} Build and construct prototypes based on ML models, proof of concepts and present to the client, interfacing of the third-party cloud service 'Parasoft CE' for service virtualization and API-testing.  \textit{Duration: 2 months}}
        \resumeItem{\textbf{Tata Motors in vehicle industry for predictive maintenance.} - Proof of Concept \textit{Duration: 2 months}}
        \resumeItem{\textbf{{Techprocess Payment services (Ingenico group) for payment flow metrics determination.}} Generating use case and testing ML models for fraud detection for preventing transaction loss to merchants and payment optimization in areas like billing, conversion, payouts and connectivity. Key responsibilities: Present results in an intuitive, actionable manner that can be understood by all sponsor audiences and stakeholders, implementation of a middle-ware to check for payment optimization with security to the workflow. Support projects throughout their life-cycle, including conceptualization, requirements definition, data procurement, development, integration, and socialization. \textit{Duration: 6 months}}
      \resumeItemListEnd

    %\resumeSubheading
      %{Startup, Inc}{May 2019 -- August 2019}
      %{Front End Developer Intern}{City, State}
     % \resumeItemListStart
       % \resumeItem{Assisted in development of the front end of a mobile application for iOS/Android using Dart and the Flutter framework.}
        %\resumeItem{Worked with Google Firebase to manage user inputted data across multiple platforms including web and mobile apps.}
        %\resumeItem{Collaborated with team members using version control systems such as Git to organize modifications and assign tasks.}
        %\resumeItem{Utilized Android Studio as a development environment in order to visualize the application in both iOS and Android.}
    %\resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    \resumeProjectHeading
        {\textbf{Object detection using Semi-Supervised Classification} $|$ \emph{Python, OpenCV}}{Ongoing}
          \resumeItemListStart
            \resumeItem{Using the PASCAL Visual Object Classes (VOC 2007) for image classification using Semi-Supervised learning technique.}
            \resumeItem{Extracting key features like Visual BOW, SURF, SIFT, MPEG-7 Color Layout Descriptor.}
            \resumeItem{ Implementation of a Semi-Supervised learning algorithm to classify based on the above features and present the results in form a conference poster.}
            %\resumeItem{As an alternative also Dockerized this application to decommission the need of storing onto local setup or virtual environment.}
          \resumeItemListEnd
          \vspace{-13pt}
        \resumeProjectHeading
          {\textbf{Psychological and Behavioural distress of Covid-19 and Infodemics} $|$ \emph{R, Shiny apps}}{April 2021}
          \resumeItemListStart
            \resumeItem{Semester-long Data Science project in R for understanding the mental distress of population and sub-population across the globe.}
            \resumeItem{Diagnostic analysis included the survey data regarding the patterns of peoples behaviour and trends indicating the stress level.}
            \resumeItem{ At a prescriptive level, `emoji-bot` for analyzing the user behaviour when interacting with the shiny application.}
            %\resumeItem{As an alternative also Dockerized this application to decommission the need of storing onto local setup or virtual environment.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Pandemic Prediction} $|$ \emph{Python, Flask, Docker, Heroku}}{September 2020}
          \resumeItemListStart
            \resumeItem{A simple linear regression machine learning model for predicting the total cases of pandemic from OWID dataset.}
            \resumeItem{Built using Python libraries (Pandas, NumPy, Statsmodels, Pickle, Matplotlib, Seaborn).}
            \resumeItem{Model is further represented as a Flask Web Application with a backend database connectivity to SQLite3 using SQLAlchemy.}
            \resumeItem{ Later deployed to Heroku PaaS on Cloud Platform (webserver: Waitress, version control: git).}
            \resumeItem{As an alternative also Dockerized this application to decommission the need of storing onto local setup or virtual environment.}
          \resumeItemListEnd
          \vspace{-13pt}
          \newpage
      \resumeProjectHeading
          {\textbf{Emoji.Voto} $|$ \emph{Kubernetes, Docker}}{September 2020}
          \resumeItemListStart
            \resumeItem{A simple example application containing three dockerized microservices and a website.}
            \resumeItem{Website illustrating list of emojis you can vote for and a leaderboard with the emojis with the highest votes with the full-fledged application running on Kubernetes cluster.}
            \resumeItem{Application environment was on Linux, Ubuntu 18.04 distribution. Kubernetes components used: Ingress, Helm, Pods, Deployments, Services, Horizontal Pod Autoscaler.}
          \resumeItemListEnd 
          \vspace{-13pt}
          \resumeProjectHeading
          {\textbf{Demorpher - Scientific Team Project} $|$ \emph{Java, Eclipse, Android}}{August 2020}
          \resumeItemListStart
            \resumeItem{Android application to detect morphed passport images.(Development of Android application called 'Demorpher' which takes the user image and compares with a pre-existing morphed image using NFC and JMRTD.}
            \resumeItem{The resultant would produce the demorphed image with matching accuracy.}
           % \resumeItem{Implemented object-oriented programming practices such as inheritance to create different account types and databases.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-15pt}


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Java, R, HTML/CSS, JavaScript, SQL} \\
     \textbf{Developer Tools}{: VS Code, Git, Heroku, R Studio, Spyder, Gephi} \\
     \textbf{Technologies/Frameworks}{: Linux, Kubernetes, GitHub, Docker, OpenCV, NLTK, Tensorflow} \\
    }}
 \end{itemize}
 \vspace{-16pt}


%-----------INVOLVEMENT---------------
\section{Publications / Talks}
    \resumeSubHeadingListStart
        \resumeSubheading{Technical Reports}{Fall 2019 -- Present}{Experimental Findings}{Otto von Guericke University}
            \resumeItemListStart
                \resumeItem{Ranjiraj Rajendran Nair \& Darshit Paresh Shah \&  Nikhilkumar Italiya \& Endi Haxhiraj (2020). "Android Application for detecting morphed passport images". In: \textit{WTP IT Security}, Otto von Guericke University, August 28-08, 2020..}
                \resumeItem{Ranjiraj Rajendran Nair \& Darshit Paresh Shah (2019). \textit{"Bio-metric benchmark based on handwriting and hand geometry Modalities"}. Otto von Guericke University, January 22-01, 2019.}
            \resumeItemListEnd
    
    \resumeSubHeadingListStart
        \resumeSubheading{Publications}{2018}{Books}{Datta Meghe College of Engineering}
            \resumeItemListStart
                \resumeItem{Ranjiraj Rajendran Nair (2018). "Analysis of Algorithms". In: \textit{Essential Data structure algorithms for computer scientists}, University of Mumbai, October 12-10, 2018.}
                \resumeItem{Ranjiraj Rajendran Nair (2018), "Operating Systems". In: \textit{In between hardware and software}, University of Mumbai, October 12-10, 2018.}
                \resumeItem{Ranjiraj Rajendran Nair (2018). "Computer Organization and Architecture". In: \textit{The power of cores}, University of Mumbai, October 12-10, 2018.}
                \resumeItem{Ranjiraj Rajendran Nair (2017). "C language Basics". In: \textit{The Structured Programming Approach}, University of Mumbai, July 09-07, 2017.}
                
            \resumeItemListEnd
        
    \resumeSubHeadingListEnd
    
    \resumeSubHeadingListEnd
    
    \resumeSubHeadingListStart
        \resumeSubheading{Talks}{2018}{Seminar}{Datta Meghe College of Engineering}
            \resumeItemListStart
                \resumeItem{Building your path towards Data Science.}
            \resumeItemListEnd
        
    \resumeSubHeadingListEnd
    
    \resumeSubHeadingListStart
        \resumeSubheading{Talks}{2017}{Demonstrative speaking}{QualityKiosk Technologies}
            \resumeItemListStart
                \resumeItem{Quarterly Knowledge Transfer session in Service Virtualization and API testing.}
            \resumeItemListEnd
        
    \resumeSubHeadingListEnd


\end{document}
